\section{Required Materials.}

Aside from the board itself, each player will get 20 square tiles.
The tiles should be seperated into sets of 4, giving each player a 5 sets of tiles.

\section{Preparing for Play.}

The players will then proceed to arrange each set of tiles into a pattern.
The tiles must be connected in such a way that all the tiles in a given set are connected on a side.
This configuration cannot be changed later on in the game, and when units are moved, the entire configuration moves as one.

Every unit must be placed on the grid at the start of play.
A valid starting position is anywhere where at least one tile of a unit is touching the edge of that player's side of the board.

\section{Taking a Turn.}

\subsection{Moving.}

On each turn, the players can make one move for each unit they control.
The movement in each turn can be any combination of horizontal or vertical shifts, or 90-degree rotations.
Moving the unit a single square vertically or horizontally is a shift.
To rotate a unit, choose one tile in the unit and turn the entire unit 90-degrees around that tile.
Units can never end in a position where any tiles overlap the tiles of another unit.
Every unit can make (6 - size) movements per turn.

\subsection{Attacking.}

Units may attack out to two squares away from themselves.
The attack must be evaluated horizontally or vertically out from the unit on the grid.
The attack starts from each tile of the unit perpendicular to the direction of the attack.

The range may be modified by unit configuration as well as by whatever ground effects the unit may have.

If there are two or more tiles in the line that the attack is firing out from, each tile beyond the first confers an additional one square's range to the attack.
Thus, if a unit has three tiles arranged in a line, and fires parallel to that line, the attack has a range of four squares.

When a unit is within an attack range, the unit has taken a hit.
The player who was attacked is allowed to pick a single tile to remove from his unit.
The block must be chosen so that the remaining tiles in the unit are still connected to each other.
The unit is considered to be dead when its last tile is hit.

\subsection{Ground Effects.}

At all times, units will have ground effects on them.
Which particular effects the unit has on it at any given time depends on its position.
Check the color of the grid underneath the unit to determine which effect that particular square has.
The effects of all squares that the unit is located are always applied.

\begin{description}
\item[Yellow] squares confer an additional 1 square's range to the unit's attack.
\item[Red] squares confer an additional 1 movement during any turn where the unit starts movement from a position containing a red square.
\item[Blue] squares allow a unit to include any adjacent friendly unit's configuration as part of its own for range determinations.
\end{description}

\section{Victory Condition.}

The players take turns attacking each other until either one player's units have been annihilated, or when the players agree to end the game.
In the latter case, the player with more total tiles still in play wins.

