%% First act should introduce characters and end with the protagonist deciding
%% to deal with the major conflict.

\extslug[day]{Gate to the Underworld}

A small booth in the middle of what appears to be a featureless gray plain.
The GATEKEEPER is standing next to the booth, looking bored.

MC wanders up, looking thoughtful.

\begin{dialogue}{Gatekeeper}
Hail, traveler.
Come over here so that I can handle the paperwork.
\end{dialogue}

\begin{dialogue}{MC}
What sort of stuff will you need?
\end{dialogue}

\begin{dialogue}{Gatekeeper}
Mm, name, reason of death\ldots
\end{dialogue}

\begin{dialogue}[hurridly]{MC}
Maybe it'd be best if I just looked at the forms.
\end{dialogue}

Gatekeeper pushes some papers towards MC.

MC looks through them.

\begin{dialogue}{MC}
Seems straightforward.
Out of curiousity, what do you do here?
It doesn't seem like the sort of post that requires a lot of attention.
\end{dialogue}

\begin{dialogue}{Gatekeeper}
It doesn't.
But I must admit that it allows me a chance to indulge in a personal interest of mine.
I had to pull quite a few favors to get a position here.
\end{dialogue}

\begin{dialogue}{MC}
Really?
Well, forgive me for my inexperience, but, well, having never died before\ldots
\end{dialogue}

\begin{dialogue}{Gatekeeper}
\ldots You were interested in what's beyond here?
Ho! You're in luck.
I have an excellent collection of stories.
All who pass by me leave their life stories with me.
I enhance my repository with the memories of those from the other side as well!
\end{dialogue}

