%% Protagonist encounters obstacles.
%% First culmination. Protagonist nears to his goal but fails and seems
%% farther from success than ever.

\extslug[night]{Underworld Proper}

A dready and nondescrepit area.
Looks like a gray an drab mirror of the living world.

Not much happens here, there is no wind or breeze.

\begin{dialogue}[VO]{Gatekeeper}
Really, I don't think I could call this Underworld much more than\ldots
oh, some elaborate holding area.
\end{dialogue}

A small group of dead spirits amble by.

\begin{dialogue}[VO]{Gatekeeper}
At best, I suppose you could say that people exist here because there's nowhere else to go.
Living people tend to be far more interesting than the dead.
\end{dialogue}

\extslug[day]{Gate to the Underworld}

Gatekeeper does a bored shrug.

\begin{dialogue}{MC}
Do all living people pass through here?
\end{dialogue}

\begin{dialogue}{Gatekeeper}
Well, not necessarily here, specifically.
And I suppose it's possible that someone may not get found and put inside.
But that'd be rare, I think.
\end{dialogue}

MC looks impressed.

\begin{dialogue}{MC}
You must really see all sorts coming through, all the same, yes?
Any really neat people you've met?
\end{dialogue}

Gatekeeper puffs up with pride and hauls out a heavy tome.
He locates a specific section in it and reads.

\begin{dialogue}{Gatekeeper}
Well\ldots
\end{dialogue}

\extslug[night]{Gate to the Underworld}

There's a heavy fog hanging over the scene.

A magician in robes and a pointy hat is accosting the Gatekeeper.

\begin{dialogue}{Magician}
Hah!
Well, if I can win this game, then I'm just going to leave.
You can't force me into that realm!
\end{dialogue}

Gatekeeper shrugs and sighs.

\begin{dialogue}{Gatekeeper}
I'll grant that challenging me to a game to earn your right to walk away is a rather traditional maneuver.
However, could you have not picked a better time for this?
\end{dialogue}

Gatekeeper motions towards a long line of spirits waiting for their turn to be processed.

\begin{dialogue}{Magician}
Well, they're ending up exactly where they're headed.
I wouldn't think it matters much when they get there, really.
\end{dialogue}

\begin{dialogue}[grumpily]{Gatekeeper}
Fine, fine.
Get on with it, I've got a busy day ahead of me.
\end{dialogue}

