%% Second Culmination: Protagonist must face down the conflict directly.

%% Denouement: Falling action, returns to state of equilibrium.

\extslug[day]{Gate to the Underworld}

MC stifles laughter and cuts off the Gatekeeper's narration.

\begin{dialogue}{MC}
I would just like to point out how absolutely terrible this story is.
\end{dialogue}

\begin{dialogue}{Gatekeeper}
\ldots what?
\end{dialogue}

Gatekeeper's countenance goes from a smug expression to a scowl of rage as the MC continues speaking.

\begin{dialogue}{MC}
Well, there's no climax, no resolution, and no meaning to such a story.
It can't be more than a self-aggrandizing narrative like that\ldots
\end{dialogue}

\begin{dialogue}{Gatekeeper}
Philistine!
You know what?
I paid a lot to be able to do this, and I'm not having some\ldots idiot like yourself come along and talk back without any comprehension of my art!
\end{dialogue}

MC bursts out laughing.

\begin{dialogue}[continued]{Gatekeeper}
That does it!
On my authority, you are hereby banished to wander this world!
Maybe a few good millenia will teach you to better appreciate my efforts!
\end{dialogue}

\begin{dialogue}{MC}
Wha\ldots
\end{dialogue}

MC is cast backwards, and whips off into the distance at a speed almost imperceptible.

\extslug[day]{Middle of a Large Field}

MC is lying supine in a comfortable patch of grass.

He laughs for a moment, and resigns himself to a wry smile.

\begin{dialogue}{MC}
Well, that certainly went a lot better than I'd expected.
Touchy gatekeeper, there.
Ah, I think I'll go visit some old friends\ldots
\end{dialogue}

MC hauls himself up and walks off screen, whistling a happy tune.

