%% First act should introduce characters and end with the protagonist deciding
%% to deal with the major conflict.

%% Characters:
%% Ferra - A quick, thief-like character.
%% Dezolis - A slower, but tanky spellcaster sort.

\extslug[day]{Large Field 0}

%% Ingame character intro.

A large, rocky field, littered with the fallen bodies of various heroes.
Broken weapons and scorch marks adorn the landscape.

FERRA and DEZOLIS are facing down a large, heavily-injured minotaur.
They're both sweating, and breathing heavily.

Ferra lunges forward and cuts down the monster in a single strike.

\begin{dialogue}{Ferra}
Hah! We've done it! This combo is pretty good.
\end{dialogue}

\begin{dialogue}{Dezolis}
\paren{looting the corpses}
Yeah, that attack got pretty good after they buffed it last patch.
I'm surprised nobody else has tried this yet.
\end{dialogue}

Ferra pulls a ring off the minotaur's body and inspects it.
The ring glitters slightly.

\begin{dialogue}{Ferra}
Nice!
This one's a pretty significant upgrade for me.
I've had my current one for half of forever already.
\end{dialogue}

Ferra stands up, blinks in the sunlight, and dusts herself off.

\begin{dialogue}{Ferra}
Hey, let's try that new dungeon tomorrow.
I wanna see what sort of stuff it's got.
\end{dialogue}

\begin{dialogue}{Dezolis}
\paren{glances up at Ferra}
Sure thing.
Well, I'm going to head out now.
Talk to you later.
\end{dialogue}

\begin{dialogue}{Ferra}
See you\ldots
\end{dialogue}

Dezolis's figure sags slightly, and vanishes.

Ferra sighs.

\begin{dialogue}[continued]{Ferra}
\ldots And I'm too slow again.
Oh well.
\end{dialogue}

Ferra stands up, stands stock still for a moment, and vanishes as well.

\intslug[night]{Ferraplayer's Room}

%% Ferra's player intro.

Ferraplayer is setting at a computer desk.
There are boxes of snacks stacked up on one side of the desk, and a can of soda.
A pile of textbooks holds up some small figurines on the other side.

Ferraplayer leans back and takes a sip of soda.

\begin{dialogue}{Ferraplayer}
Well, I sure feel productive.
\end{dialogue}

He looks at a nearby clock.

\begin{dialogue}{Ferraplayer}
One already?
I have work to do.
\end{dialogue}

Ferraplayer sighs and reaches under the desk to retrieve a satchel.
He extracts various sheafs of paper from the satchel and rummages through them.

\extslug[night]{Ferraplayer's Apartment Front}

%% Show that Ferra is busy for quite some time.

The light in Ferraplayer's room casts his silhouette, bent over his work on the desk.

\extslug[day]{Large Field 1}

%% This scene should show that Dezolis has rather impressive amounts of time logged.

Dezolis is sitting on a large rock and is counting something in a sack.

Ferra pops into existance, and starts moving after a few seconds.

\begin{dialogue}{Ferra}
Heya!
\end{dialogue}

\begin{dialogue}{Dezolis}
Hey there, Ferra.
How goes things?
\end{dialogue}

\begin{dialogue}{Ferra}
Hey, I was checking our haul from yesterday.
\paren{jokingly}
I think we could retire on this stash.
\end{dialogue}

Dezolis laughs.

\begin{dialogue}{Dezolis}
If only things were so easy.
I spent some time earlier today grabbing all the reagents we need to open the gate.
You wanna head down to that dungeon now?
\end{dialogue}

\begin{dialogue}{Ferra}
Sounds good to me.
\end{dialogue}

Dezolis slings the sack over his shoulder.
Both characters begin walking, following a worn trail.

\begin{dialogue}{Ferra}
Hey, outta curiousity.
I see you on all the time.
What do you do as a job?
\end{dialogue}

\begin{dialogue}{Dezolis}
Eh?
Ah, I have my own stuff to deal with.
I think that really, it's just that my timings are flexible.
You mostly get on when I happen to be free, I think.
\end{dialogue}

\begin{dialogue}{Ferra}
Oh, don't get me wrong.
I'm hardly in a position to be ragging on someone for the amount of time they put in.
I just want whatever you're working as.
\end{dialogue}

Dezolis laughs and slaps Ferra on the back.

