\documentclass{article}

\usepackage{times}

\title{Scenes in \emph{Sexy Beast}}

\author{Marcus Meng (FLM151)}

\begin{document}

\maketitle

In shot 1 (at roughly 30:46), Don has recently arrived at Gal's villa, and is sitting around discussing a job with him.
Gal keeps attempting to turn Don down, however, Don is fairly insistent.
In the picture, both characters have roughly the same size and take up roughly the same amount of space on-screen.
This makes sense -- at this point, Don is known to be somewhat sinister and disliked by the various characters, but the exact reasons are not apparant to the viewer.
His own actions thus far are only slightly menacing, he hasn't gotten to his out-and-out sociopathic actions yet.
The balance on-screen between them makes it so that the two characters seem to be on the same level, talking to each other as (reluctant) colleagues, rather than having any given one as an aggressor.
The conversational tone of the scene is further reinforced by the camera distance -- the medium-length shot keeps it from being too personal, while allowing the viewer to focus on the two characters without distractions.

In the third shot, the various characters are standing around in the kitchen, deliberately avoiding Don.
Their discomfort at his presence is accentuated by the way the shot is set up -- various characters are placed evenly around the room, but none are centered -- no character is given significantly more focus than another.
The presence of the characters in the foreground are balanced by having their expressions and forms darkened, making them "weigh" less in the scene visually than the ones in the back, fully lighted.
The camera distance makes the scene quite impersonal; their expressions can't be seen clearly and the space between each character is accentuated, allowing their mutual discomfort to be the main focus.

\begin{thebibliography}{9}

\bibitem{web:imdb}
	\emph{Sexy Beast}, http://www.imdb.com/title/tt0203119/

\bibitem{web:tomatoes}
	Rotten Tomatoes, http://www.rottentomatoes.com/m/sexy\_beast/

\bibitem{web:mise-en-scene}
	\emph{Mis\'{e} en Scene}, http://englit.org/eiland\_shared/critical/miseenscene.htm

\end{thebibliography}

\end{document}

